### 2019-07-23 4_metg.tex
More text and fiddle with figure placement.

@@

The \emph{minimum effective task granularity}, METG(50\%), for an application $A$ is
the smallest average task granularity (i.e., task duration) such that $A$
achieves overall efficiency of at least 50\%. For example, in
compute-bound applications efficiency can be measured as the
percentage of the available FLOP/s achieved. On Cori with 1.26 TFLOP/s available per Haswell node, METG(50\%) corresponds to
the smallest task granularity achieved while maintaining at least 0.63
TFLOP/s per node. For applications not amenable to being characterized by raw FLOP/s or B/s, an application-specific measure of performance can be
used instead (e.g., mesh cells processed per second).

>>>>

Given that Task Bench permits the rapid exploration of a large space
of application scenarios, one question is how to characterize the
overall performance of the programming systems under study. As noted
earlier, the overheads of the systems we consider varies by more than
five orders of magnitude. This makes it challenging to extract useful
information from weak and strong scaling runs.

Existing studies which consider programming system efficiency
typically use the metric \emph{tasks per second} (TPS). TPS results
are difficult to interpret and apply, because the efficiency (and thus
the amount of useful work) is not constrained. When using empty
tasks~\cite{LegionTracing18}, the resulting upper bound on task
scheduling throughput fails to represent useful work within a
realistic application. With non-empty tasks, since the efficiency of
the overall application is typically not reported~\cite{Canary16,
  Armstrong14}, TPS is not a measurement of runtime-limited
performance. Large tasks may be used to hide any amount of runtime
overhead, while small tasks may result in a drop in total application
throughput even as TPS increases.

We introduce \emph{minimum effective task granularity}, or METG, an
efficiency-constrained metric for runtime-limited
performance. METG(50\%) for an application $A$ is
the smallest average task granularity (i.e., task duration) such that $A$
achieves overall efficiency of at least 50\%. For example, in
compute-bound applications efficiency can be measured as the
percentage of the available FLOP/s achieved. On Cori with 1.26 TFLOP/s available per Haswell node, METG(50\%) corresponds to
the smallest task granularity achieved while maintaining at least 0.63
TFLOP/s per node. For applications not amenable to being characterized by raw FLOP/s or B/s, an application-specific measure of performance can be
used instead (e.g., mesh cells processed per second).

@@
